## example of logistic regression

# classify student application as admit or reject
target or dependent variable 
  # admit(0-n0,1-yes)
predictors or independent variables
  # GRE
  # GPA 
  # RANK
```{r}
mydata<-read.csv(file.choose(),header=T)
str(mydata)
head(mydata)
```
# convert data into factor
```{r}
mydata$admit<-as.factor(mydata$admit)
mydata$rank<-as.factor(mydata$rank)
str(mydata)
```
# two eay table of factor variable
```{r}
xtabs(~admit+rank,data=mydata)
```
Partition data >> train & test
```{r}
library(rsample)
data_split<-initial_split(mydata)
train<-training(data_split) ## 400 variables
test<-testing(data_split)   ## 100 variables
```
## Logistic regression model 
```{r}
mymodel<-glm(admit~gre+gpa+rank,data=train,family = 'binomial')
summary(mymodel)

```
## prediction --> train data
```{r}
p1<-predict(mymodel,data=train,type = "response")
head(p1)
head(train)
```
## misclassification error -->> traindata
```{r}
pred1<-ifelse(p1>0.5,1,0)
tab1<-table(predicted=pred1,actual=train$admit)
tab1
1-sum(diag(tab1)/sum(tab1))  ## % of misclassification error
```

for testing data
```{r}
p2<-predict(mymodel,test,type="response")
head(p2)
pred2<-ifelse(p2>0.5,1,0)
tab2<-table(predicted=pred2,actual=test$admit)
tab2
1-sum(diag(tab2)/sum(tab2))
```

   